---
title: "Spanish TDT movies report"
author: "Guillermo Diaz"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_align: "left"
    toc_depth: 2
    theme: "united"
  pdf_document:
    toc: yes
    toc_depth: '2'
lang: "es-ES"
---

```{r}
#| echo = FALSE
options(knitr.table.format = "html") 
```

# Introduction

[GitHub](https://github.com/GuilleDiaz7)

This line of code is quite magical. Change any `opts_chunk` here and it will change setting for the entire document. You can set any option you want: `echo`, `include`, `warning` or `messages`.

```{r setup}
#| include = TRUE
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

\newpage

# Load and clean data

```{r Load and prepare data}
#| warning = FALSE,
#| include = FALSE,
#| messages = FALSE
library(dplyr)
library(tidyr)


data <- read.csv("https://raw.githubusercontent.com/GuilleDiaz7/Automatic-Web-Scraping-of-Spanish-TDT-Films/main/data/pelis_tv_hoy.csv", fileEncoding = 'UTF-8')

df <- data %>% mutate(
  genre = replace(genre, genre == "Suspense / Thriller", "Suspense"),
  genre = replace(genre, genre == "Documentales", "Documental"),
  genre = replace(genre, genre == "Ciencia ficci?n", "SyFy"),
  genre = replace(genre, genre == "Infantil/Familiar", "Infantil")
)
```

The data set contains `r nrow(df)` instances and `r ncol(df)` variables. From now on, we won't be using the variable `Description` and a bunch more related to the creators of the film (directors, writers, actors, etc).

```{r}
#| warning = FALSE,
#| include = FALSE
library(knitr)
library(kableExtra)
library(lubridate)

df_no_desc <- df %>% 
  select(1:8) %>% 
  mutate(date_time = as_datetime(date_time))

df_clean <- df_no_desc %>% 
  dplyr::rename(
    Date = date_time,
    Channel = channel,
    "Spanish title" = sp_title,
    "Original title" = original_title,
    Year = year,
    Genre = genre,
    Country = country,
    Length = length
  )
```

Let's see a few examples of the data

```{r}
# Hay varios temas predeterminados en kableExtra, como kable_paper()
df_clean %>% 
  head(6) %>%
  knitr::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```

# Some basic facts about the dataset

## How many films have been shown in each channel?

```{r}
library(ggplot2)

df_clean %>% 
  group_by(Channel) %>% 
  summarise(`Film count` = n()) %>%
  ggplot(aes(x = `Film count`, y = reorder(Channel, `Film count`))) +
  geom_bar(stat = 'identity') +
  theme_classic() +
  ylab("Channel")
  
```

## How many unique values there are in each variable?

```{r distinct values}
library(purrr)
df_clean %>% map_dbl(
  n_distinct) %>% 
  knitr::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```

So, if there are `r nrow(df)` instances, why do we only have `r n_distinct(df$sp_title)` movies? I guess some of them were broadcasted more than once. This is the top 10 (I filtered a couple of instances that are not films, but regular TV programs):

```{r}
df_clean %>% 
  filter(`Spanish title` != "Mejor llama a Kiko" & `Spanish title` != "El zapping de Surferos") %>% 
  group_by(`Spanish title`) %>% 
  summarise(Emisiones = n()) %>% 
  filter(Emisiones > 1) %>% 
  arrange(desc(Emisiones)) %>% 
  head(10) %>% 
  knitr::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)

```

The discrepancy between `Spanish title` (`r count(unique(df_clean["Spanish title"]))`) and `Original title` (`r count(unique(df_clean["Original title"]))`) count is striking. There must be one more duplicated value in the latter.

```{r}
df_clean %>% 
  group_by(`Original title`) %>% 
  distinct() %>% 
  filter(n()>1) %>% 
  arrange(`Original title`) %>% 
  select(3:4) %>% 
  distinct(`Spanish title`) %>% 
  mutate(Count = n()) %>% 
  filter(Count >= 2) %>% 
  select(-Count) %>% 
  knitr::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
  
```

As you can see, some different films share the same `Original title`. If this happens more times from now on, we will now. Above is the list of every film shown more than once.

# Film length

## How long are the films shown in TV?

This is the distribution of film length. The mean is `r round(mean(df_clean$Length), 0)` and the median `r round(median(df_clean$Length), 0)`.

```{r}
library(ggplot2)
df_clean %>%
  drop_na() %>%
  ggplot(aes(x = Length)) +
    geom_histogram(aes(y=..density..), binwidth = 5) +
    geom_density(alpha = 0.2, fill = "#FF6666") +
    theme_classic()

```

Let's see how it is by channel.

```{r}
df_clean %>% 
  drop_na() %>% 
  ggplot(aes(x = Length)) +
    geom_histogram(aes(y=..density..), binwidth = 5) +
    geom_density(alpha = 0.2, fill = "#FF6666") +
    facet_wrap(~ Channel) +
    theme_classic() 
```

A violin plot (a boxplot would be useful too) may be easier to interpret. It is remarkable how similar are lengths in Antena 3 channel.

```{r}
df_clean %>%  
  ggplot(aes(x = Length, y = reorder(Channel, Length, median),
             color = Channel, fill = Channel)) +
  geom_violin(size = 0.9, alpha = 0.2, show.legend = F) +
  theme_classic()
```

```{r four_shortest}
four_shortest <- df_clean %>% 
  group_by(Channel) %>% 
  summarise(Median = median(Length)) %>% 
  arrange(Median) %>% 
  slice_head(n = 4) %>% 
  select(-Median) %>% 
  as.list() %>% 
  unname() %>%
  unlist()
```

Why are `r glue::glue(four_shortest[1], ", ", four_shortest[2], ", ", four_shortest[3], " and ", four_shortest[4])` broadcasting the shortest films? Let's have a glimpse.

```{r}
library(stringr)
library(kableExtra)
library(lubridate)

df_clean %>% 
  mutate("Weekday" = weekdays.Date(Date, abbreviate = F)) %>% 
  relocate("Weekday", .after = Date) %>% 
  transmute(
    Date = Date,
    Channel = Channel,
    `Spanish title` = `Spanish title`,
    "Weekday" = case_when(
      str_detect(iconv(Weekday, to='ASCII//TRANSLIT'), regex("lunes|martes|miercoles|jueves", ignore_case = T)) ~ "Laboral",
      str_detect(iconv(Weekday, to='ASCII//TRANSLIT'), regex("viernes|sabado|domingo", ignore_case = T)) ~ "Finde"
      ),
    Length = Length
    ) %>% 
  filter(Channel == four_shortest) %>% 
  arrange(Length) %>%
  head(15) %>% 
  knitr::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```

It is obvious how short are these films; most of them are broadcasted during the afternoon, starting between 16 p.m. and 19 p.m. Most of these films are also shown on weekends (remember, including Fridays).

Now we transform `Length` in three categories being (1) less than 90 minutes, (2) between 90 and 150 minutes and (3) more than 150 minutes.

```{r}
df_clean <- df_clean %>% 
  mutate(
    length_category = case_when(
      Length <= 90 ~ "Less than 90 minutes",
      Length > 90 & Length <= 150 ~ "Between 90 and 150 minutes",
      Length > 150 ~ "More than 150 minutes",
      TRUE ~ "Rest"
    )
  )
```

#### Not color-blind graphic

```{r}
perc_data <- df_clean %>% 
    mutate(length_category = factor(length_category, levels = c("Less than 90 minutes", 
                                                      "Between 90 and 150 minutes", "More than 150 minutes"))) %>% 
  group_by(Channel) %>% 
  mutate(Channel_shown = n()) %>% 
  group_by(Channel, length_category) %>% 
  summarise(perc = n()/max(Channel_shown))

library(scales) # For percent

perc_data %>% 
  ggplot(aes(x = length_category, y = perc, fill = length_category)) +
  geom_bar(stat = 'identity', show.legend = "none") +
  facet_wrap(~ Channel) +
  geom_text(aes(label = percent(perc)), vjust = -0.2, size = 2.3) +
  theme_classic() +
  theme(axis.text.x = element_blank())
```

#### Color-blind graphic

```{r}
library(ggtext)
library(thematic)
# Color-blind safe colors
coloritos <- thematic::okabe_ito(3)
```

```{r}
perc_data %>% 
  ggplot(aes(x = length_category, y = perc, fill = length_category)) +
  geom_bar(stat = 'identity', show.legend = "none") +
  scale_fill_manual(values = coloritos) +
  facet_wrap(~ Channel) +
  geom_text(aes(label = percent(perc)), vjust = -0.2, size = 2.3) +
  theme_classic() +
  theme(axis.text.x = element_blank())
```

# By date

This is a list of the number of films shown each day.
```{r}
library(stringr)
library(kableExtra)
library(lubridate)

df_clean_film_day <- df_clean %>% 
  mutate("Weekday" = weekdays.Date(Date, abbreviate = F)) %>% 
  relocate("Weekday", .after = Date) %>% 
  transmute(
    Date = Date,
    "Weekday" = case_when(
      str_detect(iconv(Weekday, to='ASCII//TRANSLIT'), regex("lunes|martes|miercoles|jueves", ignore_case = T)) ~ "Laboral",
      str_detect(iconv(Weekday, to='ASCII//TRANSLIT'), regex("viernes|sabado|domingo", ignore_case = T)) ~ "Finde"
      )
    ) %>% 
  group_by(
    Date = as.Date(Date), Weekday) %>% 
  summarise(Films = n()) 
  

df_clean_film_day %>% 
  head(10) %>% 
  knitr::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```

There is a surprising spike on Wednesday 12th October which is not that surpring when I tell you that it is Spanish national day.

```{r}
df_clean_film_day %>% 
  ggplot(aes(x = Date, y = Films, fill = Weekday)) +
  geom_col() +
  theme_classic()
```


\newpage

# Mapping the data (or analyzing the country variable)

First, we have to prepare the data. Country names are in Spanish, let's translate them.

```{r}
unique(df_clean$Country)
```


I will check for empty values in the `Country` variable. If there isn't we will continue.

```{r}
df_clean %>% 
  filter(Country == "")

```



```{r}
df_map <- df_clean %>% 
  group_by(`Country`) %>% 
  summarise(Movies = n())

df_map <- df_map %>% 
  mutate(
    Country = case_when(
      Country == "Alemania" ~ "Germany",
      Country == "Alemania del Oeste" ~ "Germany",
      Country == "Argentina" ~ "Argentina",
      Country == "Australia" ~ "Australia",
      Country == "Bélgica" ~ "Belgium",
      Country == "Canadá" ~ "Canada",
      Country == "China" ~ "China",
      Country == "Corea del Sur" ~ "South Korea",
      Country == "Dinamarca" ~ "Denmark",
      Country == "España" ~ "Spain",
      Country == "Estados Unidos" ~ "United States of America",
      Country == "Francia" ~ "France",
      Country == "Hong Kong" ~ "Hong Kong",
      Country == "Irlanda" ~ "Ireland", 
      Country == "Islandia" ~ "Island",
      Country == "Italia" ~ "Italy",
      Country == "Noruega" ~ "Norway",
      Country == "Países Bajos" ~ "Netherlands",
      Country == "Reino Unido" ~ "United Kingdom",
      Country == "República Checa" ~ "Czech Republic",
      Country == "Rusia" ~ "Russia",
      Country == "Sudáfrica" ~ "South Africa",
      Country == "Suecia" ~ "Sweden",
      Country == "Tailandia" ~ "Tailand",
      Country == "Taiwán" ~ "Taiwan",
      Country == "Turquía" ~ "Turkey",
      Country == "Ucrania" ~ "Ukraine",
      is.na(Country) == TRUE ~ "Sin datos"
    )
  )

df_map %>% 
  arrange(desc(Movies)) %>% 
  knitr::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```

First, let's use a bar plot. Mmm, we do seem to like USA films...

```{r}
df_map %>% 
  ggplot(aes(x = reorder(Country, Movies), y = Movies)) +
  geom_bar(stat = 'identity') +
  coord_flip() +
  theme_classic()
```

Then, we plot a map.

```{r, results='hide'}
library(sf)
library(rnaturalearth)

world <- ne_countries(scale = "small", returnclass = "sf")

world %>% 
  ggplot() + 
  geom_sf() +
  geom_hline(yintercept = 0, linetype = "dashed") 

```

```{r}
world <- world %>% 
  dplyr::rename("Country" = "sovereignt")

df_world <- left_join(world, df_map)

```

Let's see how it looks filled.

```{r}
library(ggplot2)
library(sf)
df_world %>% 
  ggplot() +
  geom_sf(aes(fill = Movies)) +
  theme_void() +
  theme(legend.position = "top") +
  labs(fill = "Number of movies:") +
  guides(fill = guide_legend(nrow = 2, byrow = TRUE))
```

I will plot the same map but without United States (and maybe without Spain too). The scale is very confusing as it is.

```{r}
df_world %>% 
  filter(Country != "United States of America" & Country != "Spain") %>% 
  ggplot() +
  geom_sf(aes(fill = Movies)) +
  theme_void() +
  theme(legend.position = "top") +
  labs(fill = "Number of movies:") +
  guides(fill = guide_legend(nrow = 2, byrow = TRUE))
```


I want to see the Country distribution by channel; for example, to analize which channel promote Spanish cinema. Or how the public channels behave.


```{r}
library(forcats)
df_clean %>%
  group_by(Channel, Country) %>% 
  count(Country) %>% 
  ggplot(aes(x = fct_lump(Country, prop = 0.05), y = n)) +
  geom_col() +
  facet_wrap(~Channel) +
  coord_flip() +
  theme_classic()
```


This we we can see better how Countries are distributed within each channel.


```{r}
perc_data_2 <- df_clean %>% 
  group_by(Channel) %>% 
  mutate(Channel_shown = n()) %>% 
  group_by(Channel, Country, Channel_shown) %>% 
  summarise(perc = n()/max(Channel_shown))

perc_data_2 %>% 
  ggplot(aes(x = fct_lump(Country, prop = 0.05), y = perc)) +
  geom_col() +
  facet_wrap(~Channel) +
  coord_flip() +
  theme_classic()


```

I want to do the same but removing films from United States.

```{r}
perc_data_3 <- df_clean %>% 
  filter(Country != "Estados Unidos") %>% 
  group_by(Channel) %>% 
  mutate(Channel_shown = n()) %>% 
  group_by(Channel, Country, Channel_shown) %>% 
  summarise(perc = n()/max(Channel_shown))
  
  
perc_data_3 %>%
  ggplot(aes(x = fct_lump(Country, prop = 0.05), y = perc)) +
  geom_col() +
  facet_wrap(~Channel) +
  coord_flip() +
  theme_classic()
  
```

