---
title: "Spanish TDT movies report"
author: "Guillermo Diaz"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_align: "left"
    toc_depth: 2
    theme: "yeti"
  pdf_document:
    toc: yes
    toc_depth: '2'
lang: "es-ES"
---


```{r}
#| echo = FALSE
options(knitr.table.format = "html") 
```

# Introduction

[GitHub](https://github.com/GuilleDiaz7)

This line of code is quite magical. Change any `opts_chunk` here and it will change setting for the entire document. You can set any option you want: `echo`, `include`, `warning` or `messages`.

```{r setup}
#| include = TRUE
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

\newpage
# Load and clean data

```{r Load and prepare data}
#| warning = FALSE,
#| include = FALSE,
#| messages = FALSE
library(dplyr)
library(tidyr)


data <- read.csv("https://raw.githubusercontent.com/GuilleDiaz7/Automatic-Web-Scraping-of-Spanish-TDT-Films/main/data/pelis_tv_hoy.csv", fileEncoding = 'UTF-8')

df <- data %>% mutate(
  genre = replace(genre, genre == "Suspense / Thriller", "Suspense"),
  genre = replace(genre, genre == "Documentales", "Documental"),
  genre = replace(genre, genre == "Ciencia ficci?n", "SyFy"),
  genre = replace(genre, genre == "Infantil/Familiar", "Infantil")
)
```

The data set contains `r nrow(df)` instances and `r ncol(df)` variables. From now on, we won't be using the variable `Description`, which included a brief synopsis of each film. Let's see a few examples of the data.

```{r}
#| warning = FALSE
library(knitr)
library(kableExtra)
library(lubridate)

df_no_desc <- df %>% 
  select(1:8) %>% 
  mutate(date_time = as_datetime(date_time))

df_no_desc %>% 
  head(3) %>% 
  knitr::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```

The variables names are formatted to work with them in R, not to be shown in a document. We can clean them.


```{r}
df_clean <- df_no_desc %>% 
  dplyr::rename(
    Date = date_time,
    Channel = channel,
    "Spanish title" = sp_title,
    "Original title" = original_title,
    Year = year,
    Genre = genre,
    Country = country,
    Length = length
  )

# Hay varios temas predeterminados en kableExtra, como kable_paper()
df_clean %>% 
  head(3) %>%
  knitr::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```
# The first questions

How long are the films shown in TV?

```{r}
library(ggplot2)
df_clean %>% 
  drop_na() %>% 
  ggplot(aes(x = Length)) +
    geom_histogram(aes(y=..density..), binwidth = 5) +
    geom_density(alpha = 0.2, fill = "#FF6666") +
    theme_classic()
  
```

Let's transform length in three categories being (1) less than 90 minutes, (2) between 90 and 150 minutes and (3) more than 150 minutes.

```{r}
df_clean <- df_clean %>% 
  mutate(
    length_category = case_when(
      Length <= 90 ~ "Less than 90 minutes",
      Length > 90 & Length <= 150 ~ "Between 90 y 150 minutes",
      Length > 150 ~ "More than 150 minutes",
      TRUE ~ "Rest"
    )
  )

df_clean %>%  
  ggplot(aes(x = Length, y = reorder(Channel, Length, median), color = Channel, fill = Channel)) +
  geom_boxplot(size = 0.9, alpha = 0.2, show.legend = F) +
  theme_classic()

```



```{r}
df_clean %>% 
  group_by(Channel, length_category) %>% 
  summarise(Count = n()) %>% 
  ggplot(aes(x = length_category, y = Count, fill = length_category)) +
  geom_bar(stat = 'identity') +
  facet_wrap(~ Channel) +
  theme_classic() +
  theme(axis.text.x = element_blank())

```






¿How many unique values there are in each variable?

```{r distinct values}
library(purrr)
df %>% map_dbl(
  n_distinct
)
```

So, if there are `r nrow(df)` instances, why do we only have `r n_distinct(df$sp_title)` movies? I guess some of them were broadcasted more than once. These are the ones:

```{r}
df_clean %>% 
  group_by(`Spanish title`) %>% 
  summarise(Emisiones = n()) %>% 
  filter(Emisiones > 1) %>% 
  arrange(desc(Emisiones)) %>% 
  knitr::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)

```
# By date


```{r}
library(stringr)
library(kableExtra)
library(lubridate)

df_clean %>% 
  mutate("Weekday" = weekdays.Date(Date, abbreviate = F)) %>% 
  relocate("Weekday", .after = Date) %>% 
  transmute(
    Date = Date,
    "Weekday" = case_when(
      str_detect(iconv(Weekday, to='ASCII//TRANSLIT'), regex("lunes|martes|miercoles|jueves", ignore_case = T)) ~ "Laboral",
      str_detect(iconv(Weekday, to='ASCII//TRANSLIT'), regex("viernes|sabado|domingo", ignore_case = T)) ~ "Finde"
      )
    ) %>% 
  group_by(
    Date = as.Date(Date), Weekday) %>% 
  summarise(Films = n()) %>% 
  knitr::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)

```




```{r}
#| eval = FALSE
daily_data %>%  
  ggplot(aes(x = Date, y = Films)) +
  geom_line() +
  theme_classic()

```


\newpage
# Mapping the data

First, we have to prepare the data. Country names are in Spanish, let's translate them.

```{r}
unique(df_clean$Country)
```


```{r}
df_map <- df_clean %>% 
  group_by(`Country`) %>% 
  summarise(Movies = n())

df_map <- df_map %>% 
  mutate(
    Country = case_when(
      Country == "Alemania" ~ "Germany",
      Country == "Australia" ~ "Australia",
      Country == "Canadá" ~ "Canada",
      Country == "Dinamarca" ~ "Denmark",
      Country == "España" ~ "Spain",
      Country == "Estados Unidos" ~ "United States of America",
      Country == "Italia" ~ "Italy",
      Country == "Reino Unido" ~ "United Kingdom",
      Country == "Tailandia" ~ "Tailand",
      Country == "Corea del Sur" ~ "South Korea",
      Country == "Francia" ~ "France",
      Country == "Sudáfrica" ~ "South Africa",
      Country == "Suecia" ~ "Sweden",
      is.na(Country) == TRUE ~ "Sin datos"
    )
  )

df_map
```
First, we plot a bar plot.

```{r}
df_map %>% 
  ggplot(aes(x = Country, y = Movies))+
    geom_bar(stat = 'identity')
```


Then, we plot a map.

```{r}
library(sf)
library(rnaturalearth)

world <- ne_countries(scale = "small", returnclass = "sf")

world %>% 
  ggplot() + 
  geom_sf() +
  geom_hline(yintercept = 0, linetype = "dashed") 

```
The latter was an empty world map. We are goint to fill it with our data. We create a suitable data frame.

```{r}
world <- world %>% 
  dplyr::rename("Country" = "sovereignt")

df_world <- left_join(world, df_map)

```

Let's see how it looks filled.

```{r}
library(ggplot2)
library(sf)
df_world %>% 
  ggplot() +
  geom_sf(aes(fill = Movies)) +
  theme_void() +
  theme(legend.position = "top") +
  labs(fill = "Number of movies:") +
  guides(fill = guide_legend(nrow = 2, byrow = TRUE))
```

